\section{Linear Programming}

\begin{enumerate}
\item For Simplex Method, magically, average case polynomial time if add random Gaussian noise to the constraints. But with ellipsoid Method or Interior Point Method, it is polynomial time.
\item A linear program can be solved in a polynomial time.
\item Whenever a problem can be formulated by a linear
program, it is polynomial-time solvable
\end{enumerate}
\subsection{Duality Problem}
Use the linear combination of constraints to get the objective function.
% x1+6x2<=(m1+m3)*x1+(m2+m3)*x2
% m1+m3>1
% m2+m3>6
\begin{enumerate}
    \item For \textbf{Weak Duality Theorem}, Primal $OPT < Dual OPT$
    \item for \textbf{Strong Duality Theorem}, Primal OPT = Dual OPT. % see proof in slides-18
    \item 
\end{enumerate}

Maximum matching 
\[
    maximize \sum_{e \in E} x_e(\uparrow x)\\
    \sum_{e=(u,v) \in E}x_e\leq 1 (\forall u \in V)\\(Ax=b, A:incidence matrix,b:\uparrow) \text{for vertex u, at most one edge is selected:incidence matrix} \\
    x_e\geq 0 \text{every edge will be selected only once}\\
\]
Consider a triangle case, the maximum matching is 1, but the maximum independent set is 2. 
But by algorithm, for maximum matching and min vertex cover, edges(vertice) have 0.5, but is meaningless.
minimum vertex cover
\[
    min  \sum{u\in V} x_u\\
    x_u+x_v\geq 1
    x_u\geq 0
    \]
The problem is, how to guarantee that the optim. sol. is int?
\subsection{Strong LP-Duality and max-flow-min-cut}
\begin{itemize}
    \item LP for max-flow problem:
    \[
        \begin{aligned}
        maximize & \sum_{v:(s,v)\in E} f(s,u) \\
        f(u,v)&\leq c(u,v) &(y_{uv})   \\
        \sum_{v:(v,u)\in E} f(v,u)-\sum_{w:(u,w)\in E} f(u,w)&\leq 0 &(z_u^+)\\
        -\sum_{v:(v,u)\in E} f(v,u)+\sum_{w:(u,w)\in E} f(u,w)&\leq 0 &(z_u^-)\\
        f(e)&\geq 0
        \end{aligned}
    \]
    \item dual describes the \textbf{fractional} version of min-cut problem, denote $z_u=z_u^+-z_u^-$
    \[
        \begin{aligned}
            minimize &\sum_{(s,u)\in E} c_{uv}y_{uv}\\
        y_{su}+z_u&\geq 1\\
        y_{vt}-z_v&\geq 0\\
        y_{uv}-z_u+z_v&\geq 0 (u,v\in V \setminus\{ s,t\})\\
        y_{uv}&\geq0
        \end{aligned}
    \]
    \item dual program have \textbf{integral} optimum
    Proven by totally unimodular matrix theorem.(discuss from whether no 1, one 1, -1 and 1 occurs in the matrix, maybe by induction)
    If A is totally unimodular, then feasible solution of $Ax=b, x\geq 0$ is integral.

    \item apply Strong Duality Theorem to show max-flow-min-cut
    We will prove that $A$ is totally unimodular.
\end{itemize}
